---
title: "BILGER-HANS-ADA-HOMEWORK-03"
author: "Hans Bilger"
date: "March 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Problem 1

```{r}
####Write a simple R function you call Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data, using the following guidelines.


Z.prop.test <- function(p0, p1, p2, n1, n2, alternative="two.sided", conf.level=0.95) {
  if(is.null(p2) | is.null(n2)) {
z <- (p1 - p0)/sqrt(p0 * (1 - p0)/n1)
z
p <- pnorm(z, lower.tail = TRUE)
p
lower <- p1 - qnorm(1-(1-conf.level)/2) * sqrt(p1 * (1 - p1)/n1)
upper <- p1 + qnorm(1-(1-conf.level)/2) * sqrt(p1 * (1 - p1)/n1)
ci <- c(lower, upper)
ci
  if((n1 * p0 > 5) & (n1 * (1-p0) >5)) {
    print("Either n1 * p0 > 5 or n* (1-p0) >5. Because of this, it may be invalid to assume the normal     distribution.")
    }
  } else {
pstar <- p1*(n1/(n1+n2)) + p2*(n1/(n1+n2))
z <- (p2 - p1)/sqrt(pstar * (1 - pstar)) * (1/n1 + 1/n2)
z
p.upper <- 1 - pnorm(z, lower.tail = TRUE)
p.lower <- pnorm(z, lower.tail = FALSE)  # two-tailed probability, so we add the upper and lower tails
p <- p.upper + p.lower
p
lower <- (p2-p1) - qnorm(1-(1-conf.level)/2) * sqrt(p1 * (1 - p1)/n1)
upper <- (p2-p1) + qnorm(1-(1-conf.level)/2) * sqrt(p1 * (1 - p1)/n1)
ci <- c(lower, upper)
ci
  }
}
  
```

```{r}
p1 <- 0.6
p0 <- 0.8
n1 <- 30

z <- (p1 - p0)/sqrt(p0 * (1 - p0)/n1)
z
p <- pnorm(z, lower.tail = TRUE)
p
lower <- p1 - qnorm(0.975) * sqrt(p1 * (1 - p1)/n1)
upper <- p1 + qnorm(0.975) * sqrt(p1 * (1 - p1)/n1)
ci <- c(lower, upper)
ci

pt <- prop.test(x = 18, n = 30, p = 0.80, conf.level = 0.95, alternative = "less", 
    correct = FALSE)  # use correct=FALSE if we satisfy that n*pi and n*(1-pi) are both >5
pt
```
####Your function should take the following arguments: p1 and n1 (no default) representing the estimated proportion and sample size (e.g., based on your sample data); p2 and n2 (both defaulting to NULL) that contain a second sample’s proportion and sample size data in the event of a two-sample test; p0 (no default) as the expected value for the population proportion; and alternative (default “two.sided”) and conf.level (default 0.95), to be used in the same way as in the function t.test().

####When conducting a two-sample test, it should be p1 that is tested as being smaller or larger than p2 when alternative=“less” or alternative=“greater”, respectively, the same as in the use of x and y in the function t.test().

####The function should perform a one-sample Z-test using p1, n1, and p0 if either p2 or n2 (or both) is NULL.

####The function should contain a check for the rules of thumb we have talked about (n×π>5 and n×(1−π)>5) to ensure the validity of assuming the normal distribution in both the one- and two-sample settings. If this is violated, the function should still complete, but it should also print an appropriate warning message.

The function should return a list containing the following elements: Z (the test statistic), P (the appropriate p value), and CI (the two-sided CI with respect to “conf.level” around p1 in the case of a one-sample test and around p2-p1 in the case of a two-sample test). For all test alternatives (“two.sided”, “greater”, “less”), calculate symmetric CIs based on quantiles of the normal distribution rather than worrying about calculating single-limit confidence bounds.




```